\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{University of Queensland} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge Epistasis follow-up \\[0.3cm] \huge *** summary *** \\ \horrule{2pt} \\[0.5cm] \date{}

### 2015-02-18 investigation/docs/overview.tex
updtaes to scripts and report

\begin{figure}[H]
\centering
\includegraphics[width=3.5in]{lambda_107.png}
\caption*{Figure | p-value distribution - ok}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=3.5in]{lambda_305.png}
\caption*{Figure | p-value distribution - bad}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=4in]{lambda.png}
\caption*{Figure | Distribution of median lambda from the 501 fixed SNP analysis. Red denotes original pairs identified from filter 2 - i.e. no previous study-wide additive effects. Black denotes the original filter 1 pairs}
\end{figure}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\begin{figure}[H]
\centering
\includegraphics[width=3.5in]{lambda_107.png}
\caption*{Figure | Example of p-value distribution - ok}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[width=3.5in]{lambda_305.png}
\caption*{Figure | Example of p-value distribution - bad}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\begin{figure}[H]
\centering
\includegraphics[width=4in]{lambda.png}
\caption*{Figure | Distribution of median lambda from the 501 fixed SNP analysis. Red denotes original pairs identified from filter 2 - i.e. no previous study-wide additive effects. Black denotes the original filter 1 pairs}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\begin{figure}[H]
\centering
\includegraphics[height=3in]{empF.png}
\caption*{Figure | The F-statistic corresponding to $p=4.48^{-6}$ and df1=4, df2=842 from a $H_0$ table is 7.67. This figure shows the empirical (ranked) F-statistic corresponding to $n * 4.48^{-6}$. Where $n * 4.48^{-6} < 1$, the largest F-statistic taken.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics[height=3in]{empPval.png}
\caption*{Figure | The -log10 p-values corresponding to above F-statistics (df1=4, df2=842). The -log10 $p=4.48^{-6} = 5.35$}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage

\begin{figure}[H]
\centering
\includegraphics[width=4in]{Npairs_above_empthres.png}
\caption*{Figure | For each pair (n=501) the number of tests where the test statistic is greater than the 95th percentile of an F-dist}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
